---
title: "Assignment 4 Data Analytics Project"
author: "Sandeep Tom"
date: "12/12/2021"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---
1.	Discuss the business problem/goal :The goal of this analysis is to conduct a sentiment analysis of movie ratings from IMDB website. 
2.identify where the dataset was retrieved from: For this we will be using 50,000 ratings that were available from their website to conduct the visualizations.
```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(knitr)
library(bslib)
library(dplyr)
library(expss)
library(lubridate)
library(tidytext)
library(ggplot2)
library(scales)

```
3.	The code that imported and saved  dataset in R is below
```{r, echo=FALSE}
imdb_ratings <- read_tsv("data.tsv", na = "\\N", quote = '')
head(imdb_ratings)
```
4.	describe your data set (using the common attributes such as #rows, #columns, variable names, types, means, SD, min/max, NAs, etc...) 
```{r}
summary(imdb_ratings)
```
5. The data is available on the IMDB website that contains rating information for title and the number of votes each of those titles received. From review of the dataset it looks like all missing values were removed from the dataset. For datasets of these sizes on of the key issues would be missing values / missing ratings. The dataset we are working with have had all missing values removed from them.

6. Modelling - Below we will be using visualizations techniques to analysis and gather insights from the data.


7.
Below is a graph of the ratings of all the movies by the number of votes they received in IMDB. The plot below gives you an idea of how each of those titles were voted but does not give you a very clear idea due to the volume of the data points
```{r, include=TRUE}
ggplot(imdb_ratings, aes(x = numVotes, y = averageRating)) +
          geom_point()
```

So we use a heat map to plot the same information.The graph below gives you a slightly better picture of votes by title rating

```{r, echo=FALSE}
ggplot(imdb_ratings, aes(x = numVotes, y = averageRating)) +
          geom_bin2d() +
          scale_x_log10(labels = comma) +
          scale_y_continuous(breaks = 1:10)

```

Now we will use the movies to tie them to their ratings. For that we will first use another dataset that is avialble on website. 
 

We introduce the data and then now join this data to the existing dataset.
```{r, echo=FALSE}
imdb_ratings <- read_tsv("data.tsv", na = "\\N", quote = '')
imdb_movies <- read_tsv("data1.tsv", na = "\\N", quote = '')
imdb_ratings_new <- imdb_ratings %>% left_join(imdb_movies)
head(imdb_ratings_new)
```

```{r, echo=FALSE}
plot <- ggplot(imdb_ratings_new %>% filter(runtimeMinutes < 180, titleType == "movie", numVotes >= 10), aes(x = runtimeMinutes, y = averageRating)) +
          geom_bin2d() +
          scale_x_continuous(breaks = seq(0, 180, 60), labels = 0:3) +
          scale_y_continuous(breaks = 0:10) +
          scale_fill_viridis_c(option = "inferno", labels = comma) +
          theme_minimal(base_family = "Source Sans Pro", base_size = 8) +
          labs(title = "Relationship between Movie Runtime and Average Mobie Rating",
               subtitle = "Data from IMDb retrieved July 4th, 2018",
               x = "Runtime (Hours)",
               y = "Average User Rating",
               caption = "Visualizations for ANA-515 Project",
               fill = "# Movies")
plot
```
```{r, echo=FALSE}
plot <- ggplot(imdb_ratings_new %>% filter(titleType == "movie", numVotes >= 10), aes(x = startYear, y = averageRating)) +
          geom_bin2d() +
          geom_smooth(color="green") +
          scale_x_continuous() +
          scale_y_continuous(breaks = 1:10) +
          scale_fill_viridis_c(option = "plasma", labels = comma, trans = 'log10')
plot
```

